Food-web complexity flattens the fitness landscape of an insect herbivore

### 2018-07-02 elsevier_test/elsevier_test.tex
updating plots and analyses in ms

\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[utf8]{inputenc}
\else % if luatex or xelatex
  \usepackage{fontspec}
  \ifxetex
    \usepackage{xltxtra,xunicode}
  \fi
  \defaultfontfeatures{Mapping=tex-text,Scale=MatchLowercase}
  \newcommand{\euro}{€}
\fi
% use microtype if available
\IfFileExists{microtype.sty}{\usepackage{microtype}}{}
\usepackage{color}
\usepackage{fancyvrb}
\newcommand{\VerbBar}{|}
\newcommand{\VERB}{\Verb[commandchars=\\\{\}]}
\DefineVerbatimEnvironment{Highlighting}{Verbatim}{commandchars=\\\{\}}
% Add ',fontsize=\small' for more characters per line
\usepackage{framed}
\definecolor{shadecolor}{RGB}{248,248,248}
\newenvironment{Shaded}{\begin{snugshade}}{\end{snugshade}}
\newcommand{\KeywordTok}[1]{\textcolor[rgb]{0.13,0.29,0.53}{\textbf{#1}}}
\newcommand{\DataTypeTok}[1]{\textcolor[rgb]{0.13,0.29,0.53}{#1}}
\newcommand{\DecValTok}[1]{\textcolor[rgb]{0.00,0.00,0.81}{#1}}
\newcommand{\BaseNTok}[1]{\textcolor[rgb]{0.00,0.00,0.81}{#1}}
\newcommand{\FloatTok}[1]{\textcolor[rgb]{0.00,0.00,0.81}{#1}}
\newcommand{\ConstantTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
\newcommand{\CharTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
\newcommand{\SpecialCharTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
\newcommand{\StringTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
\newcommand{\VerbatimStringTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
\newcommand{\SpecialStringTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
\newcommand{\ImportTok}[1]{#1}
\newcommand{\CommentTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textit{#1}}}
\newcommand{\DocumentationTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
\newcommand{\AnnotationTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
\newcommand{\CommentVarTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
\newcommand{\OtherTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{#1}}
\newcommand{\FunctionTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
\newcommand{\VariableTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
\newcommand{\ControlFlowTok}[1]{\textcolor[rgb]{0.13,0.29,0.53}{\textbf{#1}}}
\newcommand{\OperatorTok}[1]{\textcolor[rgb]{0.81,0.36,0.00}{\textbf{#1}}}
\newcommand{\BuiltInTok}[1]{#1}
\newcommand{\ExtensionTok}[1]{#1}
\newcommand{\PreprocessorTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textit{#1}}}
\newcommand{\AttributeTok}[1]{\textcolor[rgb]{0.77,0.63,0.00}{#1}}
\newcommand{\RegionMarkerTok}[1]{#1}
\newcommand{\InformationTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
\newcommand{\WarningTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
\newcommand{\AlertTok}[1]{\textcolor[rgb]{0.94,0.16,0.16}{#1}}
\newcommand{\ErrorTok}[1]{\textcolor[rgb]{0.64,0.00,0.00}{\textbf{#1}}}
\newcommand{\NormalTok}[1]{#1}
\ifxetex
  \usepackage[setpagesize=false, % page size defined by xetex
              unicode=false, % unicode breaks when used with xetex
              xetex]{hyperref}
\else
  \usepackage[unicode=true]{hyperref}
\fi
\hypersetup{breaklinks=true,
            bookmarks=true,
            pdfauthor={},
            pdftitle={Food-web complexity flattens the fitness landscape of an insect herbivore},
            colorlinks=true,
            urlcolor=blue,
            linkcolor=magenta,
            pdfborder={0 0 0}}
\urlstyle{same}  % don't use monospace font for urls
\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt plus 2pt minus 1pt}
\setlength{\emergencystretch}{3em}  % prevent overfull lines
\setcounter{secnumdepth}{0}
% Pandoc toggle for numbering sections (defaults to be off)
\setcounter{secnumdepth}{0}
% Pandoc header

@@

Biological diversity -- from genes, to phenotypes, to species -- has and
continues to be shaped by the interplay between ecological and
evolutionary processes. Much of this biological diversity has been
molded by natural selection arising from species interactions, such as
resource competition (Schluter (2000)), mutualisms (Jordano (1987)), and
predation (Abrams (2000)). While there is clear evidence that pairwise
interactions can drive evolution, we also know that most species
interact with multiple species in an ecological community. Understanding
how evolutionary dynamics unfold in a community context is challenging
and eminently theoretical (({\textbf{???}}), Nuismer paper, Guimeras
paper, also McGill paper about biodiversity effects on evolution). Given
the rapid loss of species diversity we are experiencing throughout the
world (cite), we are in urgent need of work that makes and tests
predictions for how the loss of species will affect the evolutionary
process in natural communities.

Predicting the evolutionary consequences of biodiversity loss first
requires an understanding of the concommitant change in the network
structure of species interactions. Knowing the interaction network is
crucial because the loss of biodiversity, in and of itself, will not
alter evolution -- it is the associated loss of ecological interactions
that will affect evolutionary change (Janzen (1974)). For a network of
directly connected species, we would expect that the loss of species to
result in a loss of network complexity. Network complexity is a property
that describes the diversity of interactions in an ecological community
(Banasek-Richter et al. (2009)). Thus, all else equal, species loss will
decrease the diversity of interactions, resulting in a more simple
network.

@@

To characterize the shape of the fitness landscape, we quantified
selection gradients acting on each trait in simple vs.~complex food
webs. We did this by fitting separate statistical models to data from
each food-web treatment. We used generalized linear mixed models (GLMMs,
Bolker et al. (2009)) with larval survival (0 or 1) as our response
variable and measure of fitness. We specified linear and quadratic terms
for each gall trait as well as linear interaction terms between each
gall trait, as fixed effects in the statistical models. To account for
the correlated structure of clutch size (gall level) and female
preference (plant level) as well as any other independent effects of
willow genotype on larval survival, we specified gall ID nested within
plant ID nested within plant genotype as random intercepts in our
statistical models. Since we were interested in characterizing the
fitness landscape -- the relationship between mean trait values and
population mean fitness -- we assumed the mean value of our random
effects (i.e.~setting them to zero) to estimate selection gradients. We
then used the method of Frederic J Janzen and Hal S Stearn (1998) to
calculate directional (\(\beta_{z_i}\)), nonlinear (\(\gamma_{z_i}\)),
and correlational (\(\gamma_{z_i,z_j}\)) selection gradients and used
parametric bootstrapping (1000 replicates) to calculate their 95\%
confidence intervals (Bolker et al. (2009)). To test whether selection
gradients differed between treatments, we used our bootstrapped
estimates to calculate the probability that selection gradients in the
simple food web were larger/smaller than in the complex food web
(i.e.~the p-value). All analyses and visualizations were conducted in R.

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{# note that I've switched to using the lme4 package to analyzing the GLMM}

\CommentTok{# GLMM ----}
\NormalTok{glmer_control <-}\StringTok{ }\KeywordTok{glmer}\NormalTok{(gall_survival }\OperatorTok{~}\StringTok{ }\NormalTok{sc.gall_size }\OperatorTok{+}\StringTok{ }\NormalTok{sc.clutch_size }\OperatorTok{+}\StringTok{ }\NormalTok{sc.female_preference }\OperatorTok{+}
\StringTok{                         }\KeywordTok{I}\NormalTok{(sc.gall_size}\OperatorTok{^}\DecValTok{2}\NormalTok{) }\OperatorTok{+}\StringTok{ }\KeywordTok{I}\NormalTok{(sc.clutch_size}\OperatorTok{^}\DecValTok{2}\NormalTok{) }\OperatorTok{+}\StringTok{ }\KeywordTok{I}\NormalTok{(sc.female_preference}\OperatorTok{^}\DecValTok{2}\NormalTok{) }\OperatorTok{+}
\StringTok{                         }\NormalTok{sc.gall_size}\OperatorTok{:}\NormalTok{sc.clutch_size }\OperatorTok{+}\StringTok{ }\NormalTok{sc.gall_size}\OperatorTok{:}\NormalTok{sc.female_preference }\OperatorTok{+}\StringTok{ }\NormalTok{sc.clutch_size}\OperatorTok{:}\NormalTok{sc.female_preference }\OperatorTok{+}
\StringTok{                           }\NormalTok{(}\DecValTok{1}\OperatorTok{|}\NormalTok{Genotype}\OperatorTok{/}\NormalTok{Plant_Position}\OperatorTok{/}\NormalTok{Gall_Number),}
                         \DataTypeTok{data =}\NormalTok{ control_df,}
                         \DataTypeTok{family =} \KeywordTok{binomial}\NormalTok{(}\DataTypeTok{link =}\NormalTok{ logit), }\DataTypeTok{optimizer =} \StringTok{"bobyqa"}\NormalTok{)}
\CommentTok{# summary(glmer_control)}

\CommentTok{# Mean fitness ----}
\NormalTok{Wbar_control <-}\StringTok{ }\KeywordTok{inverse_logit}\NormalTok{(}\KeywordTok{fixef}\NormalTok{(}\KeywordTok{update}\NormalTok{(glmer_control, .}\OperatorTok{~}\NormalTok{. }\OperatorTok{-}\NormalTok{sc.gall_size }\OperatorTok{-}\NormalTok{sc.clutch_size }\OperatorTok{-}\NormalTok{sc.female_preference)))}

\CommentTok{# Confidence intervals for selection gradients ----}
\NormalTok{boot_Beta_control <-}\StringTok{ }\KeywordTok{bootMer}\NormalTok{(glmer_control, }\DataTypeTok{FUN =}\NormalTok{ Beta_avg_grad, }\DataTypeTok{nsim=}\DecValTok{100}\NormalTok{, }\DataTypeTok{parallel=}\StringTok{"multicore"}\NormalTok{, }\DataTypeTok{ncpus=}\DecValTok{32}\NormalTok{)}

\NormalTok{## Summary ----}
\NormalTok{summary_Beta_glmm_control <-}\StringTok{ }\KeywordTok{data.frame}\NormalTok{(}
  \DataTypeTok{Phenotype =} \KeywordTok{c}\NormalTok{(}\StringTok{"Gall size"}\NormalTok{, }\StringTok{"Clutch size"}\NormalTok{, }\StringTok{"Female preference"}\NormalTok{),}
  \DataTypeTok{Food_Web =} \StringTok{"Complex"}\NormalTok{,}
  \DataTypeTok{Model =} \StringTok{"GLMM"}\NormalTok{,}
  \DataTypeTok{Beta =} \KeywordTok{round}\NormalTok{(}\KeywordTok{Beta_avg_grad}\NormalTok{(glmer_control),}\DecValTok{3}\NormalTok{),}
  \DataTypeTok{lower_2.5 =} \KeywordTok{round}\NormalTok{(}\KeywordTok{apply}\NormalTok{(boot_Beta_control}\OperatorTok{$}\NormalTok{t, }\DecValTok{2}\NormalTok{, }\DataTypeTok{FUN =} \ControlFlowTok{function}\NormalTok{(bootstraps) }\KeywordTok{quantile}\NormalTok{(bootstraps, }\FloatTok{0.025}\NormalTok{)),}\DecValTok{3}\NormalTok{),}
  \DataTypeTok{upper_97.5 =} \KeywordTok{round}\NormalTok{(}\KeywordTok{apply}\NormalTok{(boot_Beta_control}\OperatorTok{$}\NormalTok{t, }\DecValTok{2}\NormalTok{, }\DataTypeTok{FUN =} \ControlFlowTok{function}\NormalTok{(bootstraps) }\KeywordTok{quantile}\NormalTok{(bootstraps, }\FloatTok{0.975}\NormalTok{)),}\DecValTok{3}\NormalTok{)) }

\NormalTok{summary_Beta_glmm_control}
\end{Highlighting}
\end{Shaded}

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{## GLMM ----}
\NormalTok{glmer_treatment <-}\StringTok{ }\KeywordTok{glmer}\NormalTok{(gall_survival }\OperatorTok{~}\StringTok{ }\NormalTok{sc.gall_size }\OperatorTok{+}\StringTok{ }\NormalTok{sc.clutch_size }\OperatorTok{+}\StringTok{ }\NormalTok{sc.female_preference }\OperatorTok{+}
\StringTok{                         }\KeywordTok{I}\NormalTok{(sc.gall_size}\OperatorTok{^}\DecValTok{2}\NormalTok{) }\OperatorTok{+}\StringTok{ }\KeywordTok{I}\NormalTok{(sc.clutch_size}\OperatorTok{^}\DecValTok{2}\NormalTok{) }\OperatorTok{+}\StringTok{ }\KeywordTok{I}\NormalTok{(sc.female_preference}\OperatorTok{^}\DecValTok{2}\NormalTok{) }\OperatorTok{+}
\StringTok{                         }\NormalTok{sc.gall_size}\OperatorTok{:}\NormalTok{sc.clutch_size }\OperatorTok{+}\StringTok{ }
\StringTok{                          }\NormalTok{sc.gall_size}\OperatorTok{:}\NormalTok{sc.female_preference }\OperatorTok{+}\StringTok{ }
\StringTok{                           }\NormalTok{sc.clutch_size}\OperatorTok{:}\NormalTok{sc.female_preference }\OperatorTok{+}
\StringTok{                           }\NormalTok{(}\DecValTok{1}\OperatorTok{|}\NormalTok{Genotype}\OperatorTok{/}\NormalTok{Plant_Position}\OperatorTok{/}\NormalTok{Gall_Number),}
                         \DataTypeTok{data =}\NormalTok{ treatment_df,}
                         \DataTypeTok{family =} \KeywordTok{binomial}\NormalTok{(}\DataTypeTok{link =}\NormalTok{ logit), }\DataTypeTok{optimizer =} \StringTok{"bobyqa"}\NormalTok{)}
\KeywordTok{summary}\NormalTok{(glmer_treatment)}

\NormalTok{## Mean fitness ----}
\NormalTok{Wbar_treatment <-}\StringTok{ }\KeywordTok{inverse_logit}\NormalTok{(}\KeywordTok{fixef}\NormalTok{(}\KeywordTok{update}\NormalTok{(glmer_treatment, .}\OperatorTok{~}\NormalTok{. }\OperatorTok{-}\NormalTok{sc.gall_size }\OperatorTok{-}\NormalTok{sc.clutch_size }\OperatorTok{-}\NormalTok{sc.female_preference)))}

\NormalTok{## Confidence intervals for selection gradients ----}
\NormalTok{boot_Beta_treatment <-}\StringTok{ }\KeywordTok{bootMer}\NormalTok{(glmer_treatment, }\DataTypeTok{FUN =}\NormalTok{ Beta_avg_grad, }\DataTypeTok{nsim=}\DecValTok{100}\NormalTok{, }\DataTypeTok{parallel=}\StringTok{"multicore"}\NormalTok{, }\DataTypeTok{ncpus=}\DecValTok{32}\NormalTok{)}

\NormalTok{## Summary ----}
\NormalTok{summary_Beta_glmm_treatment <-}\StringTok{ }\KeywordTok{data.frame}\NormalTok{(}
  \DataTypeTok{Phenotype =} \KeywordTok{c}\NormalTok{(}\StringTok{"Gall size"}\NormalTok{, }\StringTok{"Clutch size"}\NormalTok{, }\StringTok{"Female preference"}\NormalTok{),}
  \DataTypeTok{Food_Web =} \StringTok{"Simple"}\NormalTok{,}
  \DataTypeTok{Model =} \StringTok{"GLMM"}\NormalTok{,}
  \DataTypeTok{Beta =} \KeywordTok{round}\NormalTok{(}\KeywordTok{Beta_avg_grad}\NormalTok{(glmer_treatment),}\DecValTok{2}\NormalTok{),}
  \DataTypeTok{lower_2.5 =} \KeywordTok{round}\NormalTok{(}\KeywordTok{apply}\NormalTok{(boot_Beta_treatment}\OperatorTok{$}\NormalTok{t, }\DecValTok{2}\NormalTok{, }\DataTypeTok{FUN =} \ControlFlowTok{function}\NormalTok{(bootstraps) }\KeywordTok{quantile}\NormalTok{(bootstraps, }\FloatTok{0.025}\NormalTok{)),}\DecValTok{2}\NormalTok{),}
  \DataTypeTok{upper_97.5 =} \KeywordTok{round}\NormalTok{(}\KeywordTok{apply}\NormalTok{(boot_Beta_treatment}\OperatorTok{$}\NormalTok{t, }\DecValTok{2}\NormalTok{, }\DataTypeTok{FUN =} \ControlFlowTok{function}\NormalTok{(bootstraps) }\KeywordTok{quantile}\NormalTok{(bootstraps, }\FloatTok{0.975}\NormalTok{)),}\DecValTok{2}\NormalTok{)) }

\NormalTok{summary_Beta_glmm_treatment}
\end{Highlighting}
\end{Shaded}

@@

@@

More recently, researchers have begun to explore how the community
context drives evolutionary change (({\textbf{???}}); terHorst et al.
(2018)).

@@

@@

@@

>>>>

\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[utf8]{inputenc}
\else % if luatex or xelatex
  \usepackage{fontspec}
  \ifxetex
    \usepackage{xltxtra,xunicode}
  \fi
  \defaultfontfeatures{Mapping=tex-text,Scale=MatchLowercase}
  \newcommand{\euro}{€}
\fi
% use microtype if available
\IfFileExists{microtype.sty}{\usepackage{microtype}}{}
\usepackage{graphicx}
% We will generate all images so they have a width \maxwidth. This means
% that they will get their normal width if they fit onto the page, but
% are scaled down if they would overflow the margins.
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth
\else\Gin@nat@width\fi}
\makeatother
\let\Oldincludegraphics\includegraphics
\renewcommand{\includegraphics}[1]{\Oldincludegraphics[width=\maxwidth]{#1}}
\ifxetex
  \usepackage[setpagesize=false, % page size defined by xetex
              unicode=false, % unicode breaks when used with xetex
              xetex]{hyperref}
\else
  \usepackage[unicode=true]{hyperref}
\fi
\hypersetup{breaklinks=true,
            bookmarks=true,
            pdfauthor={},
            pdftitle={Food-web complexity flattens the fitness landscape of an insect herbivore},
            colorlinks=true,
            urlcolor=blue,
            linkcolor=magenta,
            pdfborder={0 0 0}}
\urlstyle{same}  % don't use monospace font for urls
\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt plus 2pt minus 1pt}
\setlength{\emergencystretch}{3em}  % prevent overfull lines
\setcounter{secnumdepth}{0}
% Pandoc toggle for numbering sections (defaults to be off)
\setcounter{secnumdepth}{0}
% Pandoc header

@@

Biological diversity -- from genes, to phenotypes, to species -- has and
continues to be shaped by the interplay between ecological and
evolutionary processes. Much of this biological diversity has been
molded by natural selection arising from species interactions, such as
resource competition (Schluter (2000)), mutualisms (Jordano (1987)), and
predation (Abrams (2000)). While there is clear evidence that pairwise
interactions can drive evolution, we also know that most species
interact with multiple species in an ecological community. Understanding
how evolutionary dynamics unfold in a community context is challenging
and eminently theoretical (Mcpeek (2017), Mazancourt, Johnson, and
Barraclough (2008), Guimarães et al. (2017), Nuismer, Jordano, and
Bascompte (2013)). Given the rapid loss of species diversity we are
experiencing throughout the world (cite), we are in urgent need of work
that makes and tests predictions for how the loss of species will affect
the evolutionary process in natural communities.

Predicting the evolutionary consequences of species loss first requires
an understanding of the concommitant change in the species-interaction
networks. Knowing the interaction network is crucial because the loss of
biodiversity, in and of itself, will not alter evolution -- it is the
associated loss of ecological interactions that will affect evolutionary
change (Janzen (1974)). For a network of directly connected species, we
would expect that the loss of species to result in a loss of network
complexity. Network complexity is a property that describes the
diversity of interactions in an ecological community (Banasek-Richter et
al. (2009)). Thus, all else equal, species loss will decrease the
diversity of interactions, resulting in a more simple network.

@@

To characterize the shape of the fitness landscape, we quantified
selection gradients acting on each trait in simple vs.~complex food
webs. We did this by fitting separate statistical models to data from
each food-web treatment. We used generalized linear mixed models (GLMMs,
Bolker et al. (2009)) with larval survival (0 or 1) as our response
variable and measure of fitness. We specified linear and quadratic terms
for each gall trait as well as linear interaction terms between each
gall trait as fixed effects in the statistical models. To account for
the correlated structure of clutch size (gall level) and female
preference (plant level) as well as any other independent effects of
willow genotype on larval survival, we specified gall ID nested within
plant ID nested within plant genotype as random intercepts in our
statistical models. Since we were interested in characterizing the
fitness landscape -- the relationship between mean trait values and
population mean fitness -- we assumed the mean value of our random
effects (i.e.~setting them to zero) to estimate selection gradients. We
then used the method of Frederic J Janzen and Hal S Stearn (1998) to
calculate directional (\(\beta_{z_i}\)), quadratic (\(\gamma_{z_i}\)),
and correlational (\(\gamma_{z_i,z_j}\)) selection gradients and used
parametric bootstrapping (1000 replicates) to calculate their 95\%
confidence intervals (Bolker et al. (2009)). To test whether selection
gradients differed between treatments, we used our bootstrapped
estimates to calculate the probability that selection gradients in the
simple food web were larger/smaller than in the complex food web
(i.e.~the p-value). All analyses and visualizations were conducted in R
(R Core Team (2018)).

\begin{verbatim}
##           Phenotype Food_Web Model Type Estimate lower_2.5 upper_97.5
## 1     Gall diameter  Complex  GLMM Beta    0.555     0.426      0.683
## 2       Clutch size  Complex  GLMM Beta    0.036    -0.090      0.169
## 3 Female preference  Complex  GLMM Beta    0.003    -0.185      0.131
## 4         Gall size   Simple  GLMM Beta    0.289     0.208      0.339
## 5       Clutch size   Simple  GLMM Beta   -0.102    -0.190     -0.010
## 6 Female preference   Simple  GLMM Beta   -0.204    -0.291     -0.097
\end{verbatim}

\begin{verbatim}
##           Phenotype Food_Web Model      Type Estimate lower_2.5 upper_97.5
## 1     Gall diameter  Complex  GLMM Quadratic    0.050    -0.084      0.164
## 2       Clutch size  Complex  GLMM Quadratic    0.000    -0.232      0.260
## 3 Female preference  Complex  GLMM Quadratic    0.032    -0.098      0.154
## 4         Gall size   Simple  GLMM Quadratic    0.090    -0.104      0.236
## 5       Clutch size   Simple  GLMM Quadratic    0.032    -0.070      0.170
## 6 Female preference   Simple  GLMM Quadratic    0.204     0.078      0.408
\end{verbatim}

\begin{verbatim}
##     Phenotype Food_Web Model          Type Estimate lower_2.5 upper_97.5
## 1 Diam,Clutch  Complex  GLMM Correlational   -0.028    -0.145      0.055
## 2   Diam,Pref  Complex  GLMM Correlational   -0.104    -0.302      0.165
## 3 Clutch,Pref  Complex  GLMM Correlational    0.004    -0.079      0.120
## 4 Diam,Clutch   Simple  GLMM Correlational   -0.106    -0.161      0.048
## 5   Diam,Pref   Simple  GLMM Correlational    0.003    -0.052      0.093
## 6 Clutch,Pref   Simple  GLMM Correlational   -0.021    -0.167      0.085
\end{verbatim}

@@

BREAK UP INTO INDIVIDUAL PIECES: E.G. GALL SIZE. THIS SHOULD BE SMALL
ENOUGH TO ALLOW CACHING

\includegraphics{elsevier_test_files/figure-latex/Plot Univariate Landscapes-1.pdf}

\includegraphics{elsevier_test_files/figure-latex/Plot Multivariate Fitness Landscape-1.pdf}

\begin{verbatim}
##              df      AIC
## beta_control  7 809.1027
## quad_control 10 814.3022
## corr_control 13 817.6910
\end{verbatim}

\begin{verbatim}
##                  df      AIC
## beta_control      7 809.1027
## glm.beta_control  4 881.0152
\end{verbatim}

\begin{verbatim}
##                           df      AIC
## beta_control               7 809.1027
## beta_control.REonlyGallID  5 816.4817
\end{verbatim}

\begin{verbatim}
##       chisq       ratio         rdf           p 
## 349.7811634   0.5025591 696.0000000   1.0000000
\end{verbatim}

\begin{verbatim}
##                df      AIC
## beta_treatment  7 619.1030
## quad_treatment 10 620.1640
## corr_treatment 13 622.3247
\end{verbatim}

\begin{verbatim}
##       chisq       ratio         rdf           p 
## 190.3351784   0.3215121 592.0000000   1.0000000
\end{verbatim}

\begin{verbatim}
##                    df      AIC
## beta_treatment      7 619.1030
## glm.beta_treatment  4 712.4146
\end{verbatim}

\begin{verbatim}
##                             df      AIC
## beta_treatment               7 619.1030
## beta_treatment.REonlyGallID  6 669.5617
\end{verbatim}

\begin{verbatim}
## Data: treatment_df
## Models:
## beta_treatment.REonlyGallID: gall_survival ~ sc.gall_size + sc.clutch_size + sc.female_preference + 
## beta_treatment.REonlyGallID:     (1 | Genotype/Plant_Position)
## beta_treatment: gall_survival ~ sc.gall_size + sc.clutch_size + sc.female_preference + 
## beta_treatment:     (1 | Genotype/Plant_Position/Gall_Number)
##                             Df    AIC    BIC  logLik deviance  Chisq
## beta_treatment.REonlyGallID  6 669.56 695.93 -328.78   657.56       
## beta_treatment               7 619.10 649.87 -302.55   605.10 52.459
##                             Chi Df Pr(>Chisq)    
## beta_treatment.REonlyGallID                      
## beta_treatment                   1  4.394e-13 ***
## ---
## Signif. codes:  0 '***' 0.001 '**' 0.01 '*' 0.05 '.' 0.1 ' ' 1
\end{verbatim}

\begin{verbatim}
## Data: treatment_df
## Models:
## glm.beta_treatment: gall_survival ~ sc.gall_size + sc.clutch_size + sc.female_preference
## beta_treatment: gall_survival ~ sc.gall_size + sc.clutch_size + sc.female_preference + 
## beta_treatment:     (1 | Genotype/Plant_Position/Gall_Number)
##                    Df    AIC    BIC  logLik deviance  Chisq Chi Df
## glm.beta_treatment  4 712.41 730.00 -352.21   704.41              
## beta_treatment      7 619.10 649.87 -302.55   605.10 99.311      3
##                    Pr(>Chisq)    
## glm.beta_treatment               
## beta_treatment      < 2.2e-16 ***
## ---
## Signif. codes:  0 '***' 0.001 '**' 0.01 '*' 0.05 '.' 0.1 ' ' 1
\end{verbatim}

@@

More recently, researchers have begun to explore how the community
context drives evolutionary change (Mcpeek (2017); terHorst et al.
(2018)).

@@

\includegraphics{elsevier_test_files/figure-latex/Univariate Absolute Fitness Landscapes-1.pdf}

\includegraphics{elsevier_test_files/figure-latex/Multivariate Absolute Fitness Landscapes-1.pdf}

@@

\hypertarget{ref-Guimaraes2017}{}
Guimarães, Paulo R, Jr, Mathias M Pires, Pedro Jordano, Jordi Bascompte,
and John N Thompson. 2017. ``Indirect Effects Drive Coevolution in
Mutualistic Networks.'' \emph{Nature} 550 (7677): 511--14.

@@

\hypertarget{ref-De_Mazancourt2008}{}
Mazancourt, C de, E Johnson, and T G Barraclough. 2008. ``Biodiversity
Inhibits Species' Evolutionary Responses to Changing Environments.''
\emph{Ecol. Lett.} 11 (4): 380--88.

\hypertarget{ref-McPeek2017}{}
Mcpeek, Mark A. 2017. \emph{Evolutionary Community Ecology}. Princeton
University Press.

\hypertarget{ref-Nuismer2013}{}
Nuismer, Scott L, Pedro Jordano, and Jordi Bascompte. 2013.
``Coevolution and the Architecture of Mutualistic Networks.''
\emph{Evolution} 67 (2): 338--54.

\hypertarget{ref-R2018}{}
R Core Team. 2018. \emph{R: A Language and Environment for Statistical
Computing}. Vienna, Austria: R Foundation for Statistical Computing.
\url{https://www.R-project.org/}.
